---
title: "finalxproject.rmd"
author: "Natalie Palmer"
date: "12/13/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

  1. A brief description of the research question and experiment (with citation to the paper, and link to find the data) 
  

      St-Amour, S., Cailhol, L., Ruocco, A. C., & Bernard, P.(2021, April 1). Acute Effect of            Physical Exercise on Negative Affect in Borderline Personality Disorder: A Pilot Study.

                          https://doi.org/10.31236/osf.io/mdcuh
                                  https://osf.io/t2egx/
  
                                  
- The aim of this study was to guage how exercise impacts negative affect in individuals with borderline personality disorder. Negative affect was induced in all participants and levels of arousal (FAS) and levels of feeling (FS) were measured before and after the negative induction strategy. 

  This report reproduces the repeated measures t test used to evaluate the effectiveness of the negative mood induction strategy performed in the experiment by Amour, Cailhol, Ruocco, and Bernard (2021).


```{r}
library(data.table)
library(papaja)
library(dplyr)
library(ggplot2)

library(readr)
arousal_feeling_scores <- read_csv("finalxproject/arousal_feeling_scores.csv")
# View(arousal_feeling_scores)

# feeling valence scores

feeling_before <- arousal_feeling_scores$feeling_before
feeling_after <- arousal_feeling_scores$feeling_after

feeling_mean_before <- 1.3
feeling_mean_after <- -.259

sd(feeling_before)
sd(feeling_after)

(feeling_before_after <- t.test(arousal_feeling_scores$feeling_before,
                        arousal_feeling_scores$feeling_after,
                        paired = TRUE))


# arousal scores

arousal_before <- arousal_feeling_scores$arousal_before
arousal_after <- arousal_feeling_scores$arousal_after

arousal_mean_before <- 5.074
arousal_mean_after <- 6.81

sd(arousal_before)
sd(arousal_after)

(arousal_before_after <- t.test(arousal_feeling_scores$arousal_before,
                        arousal_feeling_scores$arousal_after,
                        paired = TRUE))


```

2. Table of means 

```{r}

# print table of means 

knitr::kable(colMeans(arousal_feeling_scores))


```

3. Graph of means

```{r}

# feeling means

library(dplyr)

feeling_mean_scores <- c("1.29", "-0.36")

sections <- c("before", "after")
feeling_mean_scores <- c("1.29", "-0.36")

my_data <- data.frame(sections,feeling_mean_scores)

library(ggplot2)

ggplot(my_data, aes(x = sections, y = feeling_mean_scores))+
  geom_bar(stat="identity")



# arousal means

sections <- c("before", "after")
arousal_mean_scores <- c("5.07", "6.81")

my_data <- data.frame(sections,arousal_mean_scores)

library(ggplot2)

ggplot(my_data, aes(x = sections, y = arousal_mean_scores))+
  geom_bar(stat="identity")



```
