---
title: "Lab_1.Rmd"
author: "Natalie Palmer"
date: "9/20/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Compute the sum of the sequence 100 to 1000, going up by a constant value of 100
```{r}
#seq(from, to, by= )
seq(from = 100, to = 1000, by = 100)
sum( seq(100,1000,100) )
```
2. Compute the sum of these numbers       (1,3,2,4,3,5,4,3,4,5,6,5,6,7,6,5,6,5,4,3,4,5)
```{r}
x <- c(1,3,2,4,3,5,4,3,4,5,6,5,6,7,6,5,6,5,4,3,4,5)
sum(x)
```

3. Write a custom sequence generator function using a for loop that generates a sequence from a starting integer value to an ending integer value in steps of 1. Demonstrate that it can produce the sequence 1 to 10.
```{r}
X1 <- 1
Xn <- 10
step <- 1
1:10

seq(from = 1, to = 10, by = 1)

for (i in 1:10) {
  print(i)
}
```
4. Write a custom function to implement the following general equation to find the sum of any constant series:
```{r}
#seq(from, to, by= )
seq(from = 10, to = 100, by = 10)
sum( seq(10,100,10) )

X1 <- 10
Xn <- 100
step <- 10
(((Xn - X1)/step) + 1) * ((X1 + Xn)/2) 

```
5. Write a custom function that generates a constant series between any start and end values, with any constant, and finds the sum. Have your function output both the sequence and the sum. 
```{r}
10:100
seq(from = 10, to = 100, by = 10)
sum( seq(10,100,10) )

```

6. Use the sum() and the length() functions to calculate the mean (average) of the numbers x = c(1,2,3,4,5).

```{r}
# Create a vector. 
x <- c(1,2,3,4,5)
sum(x)
length(x)

# Find mean.
result.mean <-  mean(x)
print(result.mean)
```

