---
title: "Lab_9.Rmd"
author: "Natalie Palmer"
date: "11/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
1. Obtain the data from the online repository, show your code for loading it into R, then conduct the same tests reported in Experiment 1 that the authors conducted. These include one binomial test, and two chi-square tests. Briefly report your re-analysis, and discuss whether you obtained the same values as the authors did (6 points).
```{r}
library(readxl)
When_not_choosing_leads_to_not_liking_Data <- read_excel("~/Desktop/When not choosing leads to not liking_Data.xlsx")


# e1 data

library(dplyr)
e1_data <- When_not_choosing_leads_to_not_liking_Data %>%
   filter(ExperimentNumber == "1")

# binomial test

sum_C <- sum(e1_data$`Infant Chose C`)
total_C <- length(e1_data$`Infant Chose C`)

(binomial_p <- pbinom(q = total_C - sum_C,
                    size = total_C,
                    prob = .5,
                    lower.tail = TRUE)*2)

pbinom(q= 21-16, size= 21, .5, lower.tail = FALSE)*2


# chi-square for gender 

library(tidyr)

gender_choice_table <- e1_data %>%
  group_by(Gender, `Infant Chose C`) %>%
  summarize(counts = n()) %>%
  pivot_wider(names_from = c(Gender),
              values_from = counts)

gender_choice_table <- gender_choice_table[,2:3]

(gender_Xsq <- chisq.test(gender_choice_table))

uncorrected_Xsq <-
  sum((gender_Xsq$observed-gender_Xsq$expected)^2/gender_Xsq$expected)

gender_Xsq_unc <-pchisq(uncorrected_Xsq,1,lower.tail = FALSE)

# chi-square for age 

age_table <- e1_data %>%
  group_by(AgeMonths, `Infant Chose C`) %>%
  summarize(counts = n()) %>%
  pivot_wider(names_from = c(AgeMonths),
              values_from = counts) 

age_table[is.na(age_table)] <- 0
age_table <- as.matrix(age_table[,2:21])
(age_xs <- chisq.test(age_table))

age_xs$observed

```


For the most part, I did get the same results as the researchers. However, at first I got slightly different results for the chi-squared test for age where X-squared = 19.153, df = 20, p-value = 0.5119 I'm not sure why this happened/ seems like the degrees of freedom was off for some reason? 

```{r}

```

In the critical test trial that followed, 16 of the 21 infants (0.7619048%) chose the new block (block C; Fig. 1)-a percentage significantly different from chance, according to a two-tailed binomial test, p = 0.027 , 95% exact confidence interval (CI)=[52.83%,91.78%], relative risk ratio = 1.52. A chi-squared test for independence indicated no significant effect of age or gender on infants' choices, X-squared = 18.244, df = 19, p-value = 0.5062.
