---
title: "Lab5.Rmd"
author: "Natalie Palmer"
date: "10/4/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
1. Trust but verify. We trust that the rnorm() will generate random deviates in accordance with the definition of the normal distribution. For example, we learned in this lab, that a normal distribution with mean = 0, and sd =1 , should only produce values larger than 2.5 with a specific small probability, that is P(x>2.5) = 0.006209665. Verify this is approximately the case by randomly sampling 1 million numbers from this distribution, and calculate what proportion of numbers are larger than 2.5.
```{r}
pnorm(2.5, mean=0, sd=1, lower.tail = FALSE)

my_sample <- rnorm(1000000, mean=0, sd=1)

selection <- my_sample[my_sample > 2.5]
length(selection)/1000000

```

2. If performance on a standardized test was known to follow a normal distribution with mean 100 and standard deviation 10, and 10,000 people took the test, how many people would be expected to achieve a score higher than 3 standard deviations from the mean? 
```{r}

pnorm(q=130, mean = 100, sd=10, lower.tail = FALSE)

10000*pnorm(q=130, mean = 100, sd=10, lower.tail = FALSE)

# a simulation

some_observations <- rnorm(10000,mean = 100, sd=10)
length(some_observations[some_observations > 130])/10000

```

3. You randomly sample 25 numbers from a normal distribution with mean = 10 and standard deviation = 20. You obtain a sample mean of 12. You want to know the probability that you could have received a sample mean of 12 or larger.
```{r}

sampling_distribution <- replicate(10000,mean(rnorm(25, mean=10, sd=20)))
hist(sampling_distribution)

length(sampling_distribution[sampling_distribution >= 12])/10000

```

4.You randomly sample 100 numbers from a normal distribution with mean = 10 and standard deviation = 20. You obtain a sample mean of 12. You want to know the probability that you could have received a sample mean of 12 or larger.
```{r}

sampling_distribution <- replicate(10000,mean(rnorm(100, mean=10, sd=20)))
hist(sampling_distribution)

length(sampling_distribution[sampling_distribution > 12])/10000


```

5. You randomly sample 25 numbers from a normal distribution with mean = 10 and standard deviation = 20. You obtain a sample standard deviation of 15. You want to know the probability that you could have received a sample standard deviation of 15 or less.
```{r}
sampling_distribution <- replicate(10000, sd(rnorm(25, mean=10, sd=20)))
hist(sampling_distribution)

length(sampling_distribution[sampling_distribution >= 12])/10000


```