---
title: "Lab_8.Rmd"
author: "Natalie Palmer"
date: "10/25/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Write a function to convert a vector of raw-scores into z-scores. The function should have inputs for the vector, the mean and sd of the normal distribution, and should return a vector of zscores. (1 point). Also, demonstrate that the function works correctly (1 point). How you make the demonstration is up to you.

```{r}
to_zscores <- function(raw,mu,sd){
  zscores <- (raw-mu)/sd
  return(zscores)
}

some_numbers <- c(8,6,4,2,10)

to_zscores(some_numbers,6,3.16)

to_zscores_z <- function(raw,mu=NULL,sdev=NULL){
  if(is.null(mu) == TRUE) mu <- mean(raw)
  if(is.null(sdev) == TRUE) sdev <- sd(raw)
  zscores <- (raw-mu)/sdev
  return(zscores)
}

to_zscores_z(some_numbers, mu = 6, sdev = 3.16)

to_zscores_z(some_numbers)
```

2. Base R does not have a function for a z-test. Write a function to accomplish a one-sample z-test. Remember, a one-sample z test is used to compare the probability of obtaining the sample mean (or larger or smaller) if it came from a known normal distribution. (2 points).

```{r}
z.test <- function(sample_mean,sample_size,mu,sigma){
  smpl_dist_mean <- mu
  smpl_dist_sd <- sigma/sqrt(sample_size)
  
  p_value <- pnorm(sample_mean,smpl_dist_mean,smpl_dist_sd, lower.tail = FALSE)
  return(p_value)
}

z.test(sample_mean = 50,
       sample_size = 25,
       mu = 40,
       sigma = 7)

##

z.test <- function(sample_mean,sample_size,mu,sigma, two.tailed=TRUE){
  smpl_dist_mean <- mu
  smpl_dist_sd <- sigma/sqrt(sample_size)
  
  p_value <- pnorm(sample_mean,smpl_dist_mean,smpl_dist_sd, lower.tail = FALSE)
  if(two.tailed == TRUE) p_value <- p_value*2
  return(p_value)
}

z.test(sample_mean = 37,
       sample_size = 5,
       mu = 40,
       sigma = 7,
       two.tailed = FALSE)

##

z.test <- function(sample_mean,
                   sample_size,
                   mu,
                   sigma, 
                   two.tailed=TRUE){

    
  smpl_dist_mean <- mu
  smpl_dist_sd <- sigma/sqrt(sample_size)
  
  abs_difference <- abs(sample_mean - mu)
  
  p_value <- pnorm((mu+abs_difference),smpl_dist_mean,smpl_dist_sd, lower.tail = FALSE)
  
  if(two.tailed == TRUE) p_value <- p_value*2
  return(p_value)

}

z.test(sample_mean = 37,
       sample_size = 5,
       mu = 40,
       sigma = 7,
       two.tailed = FALSE)

```

