---
title: "Lab_6.Rmd"
author: "Natalie Palmer"
date: "10/13/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Write a function that conducts a randomization test for the mean difference between two groups, and show that it works. Specifically, using your function, conduct a randomization test on the same data we used in the above example from lab. Report the results and briefly discuss what the results of the randomization tell you. (6 points). Extra: if the observed mean difference in the experiment was found to be .5, what would you have concluded from the randomization test?

Confidence: 000

```{r}

group_one <- c(5,6,7,8,9)
group_two <- c(2,3,4,1,6)

randomization_test <- function(A, B, resamples = 100){
  # calculate actual means
  group_A_mean <- mean(A)
  group_B_mean <- mean(B)
  mean_difference <- group_A_mean - group_B_mean
  
  #conduct randomization 
  all_means <- c(A,B)
  
  simulated_differences <- c()
  for(i in 1:resamples){
   resample <- sample(all_means)
   new_A_mean <- mean(resample[1:length(A)])
   new_B_mean <- mean(resample[(length(A)+1):length(all_means)])
   simulated_differences[i] <- new_A_mean-new_B_mean
}
  
the_plot <- ggplot2::qplot(simulated_differences)+
  ggplot2::geom_histogram(color="orange")+
  ggplot2::geom_vline(xintercept=mean_difference, color ="red")+
  ggplot2::theme_classic()

 p_value <- length(simulated_differences[simulated_differences >=
                                mean_difference])/resamples
  


  test_output <- list(A_mean = group_A_mean,
                      B_mean = group_B_mean,
                      difference = mean_difference,
                      randomization = simulated_differences,
                      plot = the_plot,
                      p_value = p_value)
  
  return(test_output)
  
}

randomization_test(A=group_one,
                   B=group_two,
                   resamples = 100)



```



```{r}


the_data <- read.csv("open_data/SchroederEpley2015data.csv", header = TRUE)

library(dplyr)

group_0 <- the_data %>%
  filter(CONDITION == 0) %>%
  select(Intellect_Rating)


group_0 <- group_0$Intellect_Rating


group_1 <- the_data %>%
  filter(CONDITION == 1) %>%
  select(Intellect_Rating)

group_1 <- group_1$Intellect_Rating

randomization_test(A=group_0,
                   B=group_1,
                   resamples = 1000)


```

The results indicate that their is a statistically significant difference and that chance alone is unlikely to be the reason for the difference. 

