---
title: "Lab3.Rmd"
author: "Natalie Palmer"
date: "9/22/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Create five samples of 25 observations from a normal distribution with mean 200, and standard deviation 100. Compute the mean of each sample, and plot the means in a graph using ggplot2.

```{r}
# create vectors for columns 
observations <- rnorm(n = 5*25, mean = 200, sd =100)
samples <- rep(1:5, each=25)

# creates table from the above vectors using data.frame ()
my_data <- data.frame(observations,samples)

#get means of each group of samples
library(dplyr)

means <- my_data %>%
  group_by(samples) %>%
  summarize(mean_sample = mean(observations))

library(ggplot2)

ggplot(means, aes(y=mean_sample, x = samples))+
  geom_bar(stat="identity")

```

2. Additionally calculate the standard deviation of each sample from above. Use the standard deviations for error bars, and produce another graph with the means along with error bars using ggplot2. 

```{r}
observations <- rnorm(5*25, mean = 200, sd =100)
samples <- rep(1:5, each=25)
my_data <- data.frame(observations,samples)

#get means of each group of samples
means <- my_data %>%
  group_by(samples) %>%
  summarize(mean_sample = mean(observations),
            sd_sample = sd(observations))


#plot means 
ggplot(means, aes(y = mean_sample, x=samples))+
  geom_bar(stat="identity") +
  geom_errorbar(aes(ymin = mean_sample - sd_sample,
                    ymax = mean_sample + sd_sample),
                width = .25)


```


3. Demonstrate that the sample mean across a range of n, is an unbiased estimator of the population mean using a monte-carlo simulation.

```{r}
# n 2
observations <- rnorm(2*10000,mean = 10,sd =5)
samples <- rep(1:10000, each =2)
my_data <- data.frame(samples,observations)

summarized_data <- my_data %>%
  group_by(samples) %>%
  summarize(sample_means = mean(observations))

mean(summarized_data$sample_means)


# n 5
observations <- rnorm(5*10000,mean = 10,sd =5)
samples <- rep(1:10000, each =5)
my_data <- data.frame(samples,observations)

summarized_data <- my_data %>%
  group_by(samples) %>%
  summarize(sample_means = mean(observations))

mean(summarized_data$sample_means)

# n 50
observations <- rnorm(50*10000,mean = 10,sd =5)
samples <- rep(1:10000, each =50)
my_data <- data.frame(samples,observations)

summarized_data <- my_data %>%
  group_by(samples) %>%
  summarize(sample_means = mean(observations))

mean(summarized_data$sample_means)


##########
sample_sizes <- c(2,5,10,50,100)
sim_sample_means <- c()
for (i in 1:length(sample_sizes)) {
  observations <- rnorm(sample_sizes[i]*10000,mean = 10,sd =5)
  samples <- rep(1:10000, each = sample_sizes[i])
  my_data <- data.frame(samples,observations)

summarized_data <- my_data %>%
  group_by(samples) %>%
  summarize(sample_means = mean(observations))

 sim_sample_means[i] <- mean(summarized_data$sample_means)
  
}

sim_data <- data.frame(sample_sizes, sim_sample_means)

ggplot(sim_data, aes(x=sample_sizes, y=sim_sample_means, group=1))+
         geom_point()+
         geom_line() +
        coord_cartesian(ylim = c(0,20) )
    

```

4. Use a monte carlo simulation to compare the standard deviation formulas (divide by N vs N-1), and show that the N-1 formula is a better unbiased estimate of the population standard deviation, especially for small n. (2 points)

```{r}
sd_N <- function(x) {
  sqrt(sum((mean(x)-x)^2) / length(x))
}

library(dplyr)
library(ggplot2)

##########
sample_sizes <- c(2,5,10,50,100)
sim_sample_sd <- c()
sim_sample_sd_N <- c()
for (i in 1:length(sample_sizes)){
    observations <- rnorm(sample_sizes[i]*10000,mean = 10,sd =5)
    samples <- rep(1:10000, each = sample_sizes[i])
    my_data <- data.frame(samples,observations)

  summarized_data <- my_data %>%
    group_by(samples) %>%
    summarize(sample_sd = sd(observations),
              sample_sd_N = sd_N(observations))

  sim_sample_sd[i] <- mean(summarized_data$sample_sd)
  sim_sample_sd_N[i] <- mean(summarized_data$sample_sd_N)

}

sim_data <- data.frame(n = rep(sample_sizes,2) ,
                       est = c(sim_sample_sd_N,sim_sample_sd),
                       formula = c(rep("N",5), rep("N-1",5)))

ggplot(sim_data, aes(x=n, y=est, group=formula, color = formula))+
  geom_point()+
  geom_line()+
  coord_cartesian(ylim = c(0,20) )

```