---
title: "Lab_12.Rmd"
author: "Natalie Palmer"
date: "12/14/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Should you do a linear regression on this data? Explain.
Y <- c(10,9,8,7,6,5,4,3,2,1,2,3,4,5,6,7,8,9,10)
X <- c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19)

The graph shows us that the relationship is non linear. Additionally, the correlation is 0 which indicates no linear relationship, meaning no relationship. 

Usually this is an indication that a linear regression is not needed. That said, just because the relationship is not perfectly linear does not mean that there is an absence of a relationship. You could still compute one for half of the data. When split down the middle, the line on the left looks like a negative relationship wehreas the one of the right loos positive. 




```{r}


some_data <- data.frame(Y_dv= c(10,9,8,7,6,5,4,3,2,1,2,3,4,5,6,7,8,9,10),
                        X_iv= c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19))

# compute linear regression,
lm(Y_dv ~ X_iv, data=some_data)

# saving and output
save_model <- lm(Y_dv ~ X_iv, data=some_data)
summary(save_model)

cor.test(some_data$Y_dv,some_data$X_iv)


```

